Massively Parallel Learning for Penalized Logistic Regression Model

### 2013-05-30 draft.tex
add some

@@

@@

    \comment{5: The randomization design in primal map}

>>>>

The primal update contains a $\ell_1$-sampling process for the choice of $i_t$, which takes $O(n)$ time, and the update of $w_t$ takes $O(d)$ time.
The update of t can be done using a simple greedy algorithm which takes O(n) time. The primal update contains
a `2-sampling process for the choice of jt (O(d) time), and an update of
p (O(n) time). Altogether, each iteration takes O(n + d) time
    \comment{Will add more on algorithm design explanation later in next version of draft}

@@

This parallel design generally follows the framework of sequential sublinear algorithm.
It remains to have two computational components in each iteration: the primal update part from line 4 to line 12 and dual update part from line 13 to line 21.
Within the primal update part, there has been a parallel implementation period from line 4 to line 11, and also a unavoidable sequential period as illustrated in line 12.
Within the dual part, it is the same situation that a parallel implementation period from line 14 to 20 is surrounded by sequential periods for line 13 and line 21.

For the parallelization period in the \textit{primal mapreduce job}, we take advantage of the MapReduce design that takes in every data instance in the training matrix.
Instead of the fashion in the sequential algorithm that we only sample a data instance in the primal update step, we compute gradients from "almost" all data instances and make the weighted average value according to vector $\bp$ as the output gradient for update.
The details of this algorithm design is shown in \textbf{Procedure Primal-Map(inputfile)} and \textbf{Procedure Primal-Reduce(key in, value in)}.
Here, we employ a randomization when we compute those "almost" all gradients.
As you can interpret from line 7 and 8 from \textbf{Procedure Primal-Map(inputfile)}, if $r=0$, then all data instances are computed.
As the expectation value for $\bp_t{i_t}$ is $\frac{1}{n}$, we normally set $r$ to range from 0 to 1.
For the parallelization period in the \textit{dual mapreduce job}, we actually implement an embarrasingly

@@
